Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-25 paper/paper.tex
Minor edits

\section{Evaluation Metods}
\label{sec:performance}

This section describes a simulation study of the relative performance of three algorithms: DPDS, WA-DPDS, and SPSS. SPDS is not evaluated because, being a simplified version of DPDS and WA-DPDS, it will always produce results worse than the other algorithms.

@@

To evaluate and compare the algorithms, we developed a cloud workflow simulator based on CloudSim~\cite{Calheiros2011}. Our simulation model consists of Cloud, VM and WorkflowEngine entities. The Cloud entity is responsible for staring and terminating VM entities using an API similar to that used by Amazon EC2. VM entities simulate the execution of individual tasks, including randomized variations in runtime. And the WorkflowEngine entity manages the scheduling of tasks and the provisioning of VMs according to the rules established by the different algorithms. We assume that the VMs have a single core and execute tasks sequentially. Although CloudSim provides a more advanced infrastructure model which includes time-sharing and space-sharing policies, we do not use these features since we are interested mainly in the execution of tasks on VMs and high-level workflow scheduling and provisioning. The simulator reads workflow description files in a modified version of the DAX format used by the Pegasus Workflow Management System~\cite{Deelman2005}. The modified file format was created for the synthetic workflow generator developed by Bharathi, et al~\cite{Bharathi2008}.

@@

\section{Discussion of Results}
\subsection{Results Example}

>>>>

\section{Evaluation Methods}
\label{sec:performance}

@@

To evaluate and compare the three proposed algorithms, we developed a cloud workflow simulator based on CloudSim~\cite{Calheiros2011}. Our simulation model consists of Cloud, VM and WorkflowEngine entities. The Cloud entity is responsible for staring and terminating VM entities using an API similar to that used by Amazon EC2. VM entities simulate the execution of individual tasks, including randomized variations in runtime. And the WorkflowEngine entity manages the scheduling of tasks and the provisioning of VMs according to the rules established by the different algorithms. We assume that the VMs have a single core and execute tasks sequentially. Although CloudSim provides a more advanced infrastructure model which includes time-sharing and space-sharing policies, we do not use these features since we are interested mainly in the execution of tasks on VMs and high-level workflow scheduling and provisioning. The simulator reads workflow description files in a modified version of the DAX format used by the Pegasus Workflow Management System~\cite{Deelman2005}. The modified file format was created for the synthetic workflow generator developed by Bharathi, et al~\cite{Bharathi2008}.

@@

\section{Discussion of Results}

\subsection{Results Example}
